%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Himanshu Pal
\documentclass[margin,line]{resume}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{datenumber}
\usepackage{datetime}
\usepackage{hyperref}
\newdateformat{monthyeardate}{%
  \monthname[\THEMONTH], \THEYEAR}

\newcounter{dateone}
\newcounter{datetwo}

\newcommand{\difftoday}[3]{%
      \setmydatenumber{dateone}{\the\year}{\the\month}{\the\day}%
      \setmydatenumber{datetwo}{#1}{#2}{#3}%
      \addtocounter{datetwo}{-\thedateone}%
      \the\numexpr-\thedatetwo/365\relax\space year(s),
      \the\numexpr(-\thedatetwo - (-\thedatetwo/365)*365)/30\relax\space month(s)
}
%______________________________________________________________________________________________________________________

\begin{document}
\name{\Large Priyta Yadav}  \address{mobile: +91-9930145225 \\ email: yadavpriyta@gmail.com}
\begin{resume}

    \section{\mysidestyle Summary}
    Senior Automation Test Analyst, with 8.5+ years of experience managing software testing and automation projects across Retail, Core Banking and Investment Banking domains.Proven expertise in full testing life cycle including converting functional requirements to test cases, end to end release planning and execution with awareness of functional testing, regression testing, manual testing, smoke testing and user acceptance testing.   
    \section{\mysidestyle Education}

    \textbf{Hitkarni College of Engineering and Technology, Jabalpur} \hfill \textbf{2010 -- 2014}\vspace{0mm}\\\vspace{0mm}%
    \textsl{Bachelors of Engineering in Computer Science and Technology} \hfill \textsl{Percentage: 76.4}
    
    \textbf{Kendriya Vidhalaya VFJ, Jabalpur(CBSE)} \hfill \textbf{1999 -- 2010}\vspace{0mm}\\\vspace{0mm}%
    \textsl{Intermediate (Science)} \hfill \textsl{Percentage: 76.0\%}\vspace{0mm}\\\vspace{0mm}%
    \textsl{Matriculation } \hfill \textsl{Percentage: 87.4\%}
    \section{\mysidestyle Technical \\ Skills}
    \vspace{0mm}
%   \textbf{Programming Languages:} Python, JavaScript, NodeJS, C, C++, Java, Scala, Shell Script \\
    % \begin{itemize}
     \textbf{Programming Languages}: \textbf{Expert}: Java \textbf{Intermediate}: JavaScript
     
     \textbf{Testing Experience}: UI Automation Testing, REST and SOAP API Automation Testing, Regression Testing, Build Verification Testing, Behavior Driven Testing
      
      \textbf{Frameworks/Libraries/VCS:} Selenium WebDriver, TestNG, Cucumber, Selenoid Grid, Jenkins, Docker, JIRA, Swagger, JAVA Data Driven Framework, TestNG Framework, Jest, Puppeteer, JFrog Artifact Repository, Bugzilla, GitHub, Rest Assured
 
    \section{\mysidestyle Work Experience}
    \textbf{Barclays Global Service Center , Pune}\\
        \textsl{Senior Automation Test Analyst (BA4)} \hfill \textsl{July 2022 -- Present}\vspace{0mm}
        
        \begin{itemize}
            \item Led the team for UI delivery and in sprint automation, efficiently managing release from planning and execution to sign-off averaging 15+ user stories per sprint with responsbilities including prioritizing and delegating tasks to QA testers, interacting with developers and PM to communicate defects, coordinating walkthroughs with Operations team, tracking and communicating daily release progress.
            \item Built the automation from scratch using Cucumber BDD Framework and implemented features like reporting, parallel execution, Database Connections, Unix Job Executions etc.
            \item Performed Data Driven Testing using internal tool for MiFID II Post-Trade Reporting application.
            \item Built the automation for comparing new and old UI which helped in identifying data migration issues.
        \end{itemize}
    \textbf{HCL Software, Bangalore}\\
           \textsl{Automation Tester (Client: Bigfix WebUI Application, Italy)} \hfill \textsl{May 2021 -- June 2022} \vspace{1mm}%
           
        \begin{itemize}
            \item Implemented end to end automation using Jenkins including installation and configuration of Jenkins, creating pipeline jobs to run the test cases for every update of the application.
            \item Automated existing backlog of manual test cases using Jest framework and puppeteer.
            \item Designing and developing test cases which needs to be automated for regression and BVT Testing.
           \item Completed POC for executing test cases inside docker containers.
        \end{itemize}
%    \end{itemize}
    \newpage
    \section{\mysidestyle Work Experience}
    \textbf{Tata Consultancy Services, Thane}\\
           \textsl{QA Lead} \hfill \textsl{Dec 2019 -- April 2021}\vspace{0mm}\\
           \textsl{QA Analyst} \hfill \textsl{Dec 2014 -- April 2019} \vspace{0mm}\\
           \textsl{Client: The Kroger Co.(USA)} \hfill \textsl{April 2020 -- April 2021} \vspace{0mm}\\
           \textsl{Client: IDFC Bank (India)} \hfill \textsl{April 2019 -- April 2020} \vspace{0mm}\\
           \textsl{Client: Koperasi Tenera (Malaysia)} \hfill \textsl{April 2017 -- April 2019} \vspace{0mm}\\
           \textsl{Client: Mutual Trust Bank Limited (Bangladesh)} \hfill \textsl{Dec 2014 -- April 2017} \vspace{0mm}\\
    \begin{itemize}
            \item Worked as QA Lead (with team size of 5 members), responsible for implementing QA processes for defects delivery  and change requests, communicating with clients, coordinating with offshore teams and planning user acceptance testing.
            \item Built and maintained API tests using Rest Assured and TestNG framework.
            \item Executed regression and smoke testing in the branches
using Team City.
            \item Analyzed issues generated by Sonar(code quality tool) and fixing it in the automation code for enhancing code quality.
            \item Performed manual testing of Loan lifecycle, Membership modules, General ledger Recon, NPA, Payments (Pay Order, Demand Drafts, Clearing, SWIFT (Outward and Inward MT103 and MT202, Trade Finance, LC Payment, BG) etc.
       \end{itemize}
\vspace{3mm}
\section{\mysidestyle Achievements \& \\ Recognitions}\vspace{0mm}
    \begin{itemize}
             \item Received \textit{HCL Quarterly Performance Award} in Center of Excellence team for building continuous integration infrastructure and test pipelines using Jenkins.    
            \item Received \textit{TCS On The Spot Award} for ensuring reliable and timely release for KATM core banking project.
            \item Received \textit{TCS Performance Award} for IDFC Bank project.
    \end{itemize}
\vspace{1mm}
\section{\mysidestyle Certifications}
\vspace{0mm}
    \begin{itemize}
        \item Certification on Professional Automation Testing on Selenium from Squad InfoTech.
        \item Professional Scrum Master -1 Certification from Scrum.org
    \end{itemize}
\hfill \textsl{Compiled on \monthyeardate\today}
\end{resume}
\end{document}
